\chapter{About the archived documentation}
\label{About the archived documentation}

\section{Introduction to the archived chapters}

We are currently in the process to shift the book documentation
into interactive documentation modules. During this process, the
content of the book documentation is generally revised and updated.
Please refer to chapter \ref{About this documentation} for further details on this process.

Not all sections of the book documentation are already available
as interactive documentation modules.
This ``archived documentation" part contains chapters that
we think should be made interactive modules in the future. 

OpenCms 5.0 supports more than one template mechanism, and we 
recommend to use standard JSP templates instead of proprietary XML templates. 
However, most of the examples in the archived part are still only 
dealing with XML templates. 
Thus it would make little sense
to transform the documentation ``as is" into an interactive module,
because it has to be thoroughly revised. 
Moreover, the interactive documentation already available 
contains a large set of alternative examples,
to just translating and updating everything here seems to be of little value.

Nevertheless the chapter contents of the archived documentation
have been revised for OpenCms 5.0,
so for example most system path references should be up to date now,
and we also fixed typos and updated screen shots.

\section{How you can help}

In case you are interested to help in the process of transforming the 
archived chapters of the documentation into interactive modules, 
please send an email to {\em contributions@opencms.com}.